### 2014-06-13 manuscript/latitudepaper.tex
First draft of manuscript is almost done, bar graphs/tables.

%% Useful for discussion:
% These explanations for latitudinal gradients in species richness  suggest that
% other network properties should also vary over temperature and/or
% productivity, independent of species richness. Temperature affects the rate at
% which chemical reactions proceed, including metabolic reactions in organisms
% (Gillooly et al., 2001). A faster metabolism implies greater energy demands on
% an organism and therefore higher rates of herbivory, predation, and
% decomposition (Brown et al., 2004, Schemske et al., 2009). This greater
% activity tends to result in interactions with more species (Waser et al.,
% 1996, Bascompte & Jordano, 2007), increasing the number of links per species
% and connectance at higher temperatures. Reduced competition due to either
% narrower niches or a broader niche space (Davies et al., 2007) could also lead
% to higher numbers of links per species and connectance, as species are free to
% pursue links with many partners rather than being restricted to the most
% profitable links. Specialist consumers tend to be more efficient at ingesting
% and assimilating prey (Montoya et al., 2006), suggesting that specialization
% is also likely at higher latitudes where productivity is low for much of the
% year (Field et al., 1998). Higher productivity is expected to result in longer
% food chains by relaxing the upper limits set by the inefficiency of energy
% transfer across trophic levels (Brown et al., 2004). This should produce a web
% with a lower proportion of basal species and more intermediate and top
% predators in food webs. Bitrophic networks should also show more higher-
% trophic-level and animal species, since they should experience the same
% relaxed productivity in their feeding links, even if those links are not
% explicitly considered in the networks used here.

@@

A study of plant-animal mutualistic networks found the opposite trend to that observed here, that generality decreased 
with increasing latitude while increasing with increasing plant diversity \citep{Schleuning2012}. Unfortunately this 
study did not examine changes in scaling relationships over latitude... Regardless, this may indicate that food webs 
and mutualistic networks vary differently over latitudinal gradients of productivity, temperature, etc. 
\citet{Schleuning2012} propose that the latitudinal specialization gradient in mutualists derives from the gradient in 
plant diversity, as high resource diversity may lead to more generalized consumers. As species richness in the food 
webs in our dataset did not vary over latitude, it seems unlikely that this is the mechanism driving increased 
generality in high-latitude food webs. As we also observed an increase in both mean and maximum trophic level with 
latitude, it is possible that high-trophic level species are also more apt to be generalists. Generalism may be an 
important strategy for high-level consumers as their prey may be scarce or seasonal \citep{}.

>>>>

@@

A study of plant-animal mutualistic networks found the opposite trend to that observed here, that generality decreased 
with increasing latitude while increasing with increasing plant diversity \citep{Schleuning2012}. Unfortunately this 
study did not examine changes in scaling relationships over latitude... Regardless, this may indicate that food webs 
and mutualistic networks vary differently over latitudinal gradients of productivity, temperature, etc. 
\citet{Schleuning2012} propose that the latitudinal specialization gradient in mutualists derives from the gradient in 
plant diversity, as high resource diversity may lead to more generalized consumers.

A contrary argument was proposed in an earlier study \citep{Vazquez2004}. In this study, it was noted that bipartite 
networks such as plant-pollinator and host-parasite networks are typically highly nested (specialists interact with 
subsets of the interaction partners of generalists), and that nestedness tends to increase with network size 
\citep{Vazquez2004}. Therefore, as the number of species in a community increases the number of extreme specialists in 
a community should increase and generality should decrease. Importantly, this argument suggests that latitude can 
affect generality only indirectly via species richnes. As the networks in our dataset did not increase in size towards 
the tropics, and there was an effect of latitude as well as species richness, it seems unlikely that either of these 
two arguments holds.

As we also observed an increase in both mean and maximum trophic level with 
latitude, it is possible that high-trophic level species are also more apt to be generalists. Generalism may be an 
important strategy for high-level consumers as their prey may be scarce or seasonal \citep{}. These results also 
suggest that the tropics may indeed have narrower niches \citep{}. Similar increases in geographic range size with 
latitude (Rapoport's rule) have been found for mammals \citep{Letcher1994}, XX \citep{} and XX \citep{}. Large 
geographic ranges imply climactic generalization \citep{Letcher1994}, but may also promote dietary generalization 
(i.e., a species with a wide range may be more likely to eat a variety of different prey depending on what is 
available). This is supported by the fact tha feeding on many prey within a trophic level (non-omnivorous generality) 
has been shown to decrease population variability in zooplankton \citep{Romanuk2006}.
